KidsAIR wood stove grades and usage

### 2021-11-19 manuscript_tables_figures.Rmd
Minor analysis updates for main paper revisions

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  mutate(home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m")))

@@

# Character/factor data summary stats
```{r}
demographics_summary <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 | winter_id == 0) %>% 
  arrange(winter_id) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  distinct(child_id_char, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id != 2) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id != 2) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(treatment_assigned) %>% 
  mutate(area_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

# distinct by child - change var in functions above to child_id_char
char_funct_total("gender")
char_funct_area("gender")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_child")
char_funct_area("race_child")

# distinct by home - change var in functions above to home
char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_sqft_2level")
char_funct_area("home_sqft_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(winter_id == 1) %>% 
  filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(area, home, new_var) %>% 
  group_by(area) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
demographics_summary
}

@@

# Check ambient temp within groups of self-reported relative stove use
```{r}
analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds"))

@@

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  mutate(home_sqft_2level = cut(home_sqft, breaks = c(0, 1400, 100000),
                                labels = c("<130 sq m", "130+ sq m")),
         home_bedrooms = as.factor(home_bedrooms),
         home_bedrooms_cat = fct_collapse(home_bedrooms,
                                          "0" = "0",
                                          "1" = "1",
                                          "2" = "2",
                                          "3+" = c("3", "4", "5", "6", "11")))

@@

# Character/factor data summary stats
```{r}
demographics_summary <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 | winter_id == 0) %>% 
  arrange(winter_id) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  distinct(area, child_id_char, .keep_all = TRUE)

@@

demographics_summary <- data %>% 
  rename(new_var = as.factor(var)) %>% 
  filter(winter_id != 2) %>% 
  filter(area == "AK") %>% 
  #filter(treatment_assigned == "Placebo") %>%
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  filter(!is.na(child_id_char)) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent, total_n)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = as.factor(var)) %>% 
  filter(winter_id != 2) %>% 
  filter(area == "AK") %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  filter(!is.na(child_id_char)) %>% 
  mutate(total_n = n()) %>% 
  group_by(treatment_assigned) %>% 
  mutate(area_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent, area_n) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

# distinct by child - change var in functions above to child_id_char
char_funct_total("gender")
char_funct_area("gender")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_child")
char_funct_area("race_child")
char_funct_total("flu_shot")
char_funct_area("flu_shot")
char_funct_total("flu_shot_planned")
char_funct_area("flu_shot_planned")

# distinct by home - change var in functions above to home
char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_sqft_2level")
char_funct_area("home_sqft_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
char_funct_total("residents_under_five")
char_funct_area("residents_under_five")
char_funct_total("home_bedrooms_cat")
char_funct_area("home_bedrooms_cat")
```

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(area, home, new_var) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), p25 = quantile(new_var, probs = 0.25),
            med_var = median(new_var), 
            p75 = quantile(new_var, probs = 0.75),max_var = max(new_var))
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>%
  mutate(new_var = as.numeric(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>%
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Filter") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  filter(!is.na(new_var)) %>% 
  dplyr::select(treatment_assigned, home, new_var) %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), p25 = quantile(new_var, probs = 0.25),
            med_var = median(new_var), 
            p75 = quantile(new_var, probs = 0.75),max_var = max(new_var))
demographics_summary
}

@@

# Check ambient and sums temp within groups of self-reported relative stove use
```{r}
analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds"))

@@

summary_results

summary_results <- health_exposure_data_sampling_day %>% 
  select(home, area, winter_id, burn_level_3level, sums_mean_winter) %>% 
  group_by(burn_level_3level) %>% 
  summarize(mean(sums_mean_winter, na.rm = T),
            median(sums_mean_winter, na.rm = T))

### 2021-11-19 stove_grade_usage_cleaning.Rmd
Minor analysis updates for main paper revisions

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  #filter(winter_id == 1) %>% 
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = if_else(kw_hours == 1000, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected)) 
  filter(treatment_assigned == "Filter")

@@

kw_perc_exp_summary <- kids_kw_report_clean %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  #filter(area == "WMT") %>% 
  group_by(treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "25Q KW % Exp" = quantile(kw_perc_expected, 0.25),
            "Med KW % Exp" = median(kw_perc_expected),
            "75Q KW % Exp" = quantile(kw_perc_expected, 0.75),
            "Max KW % Exp" = max(kw_perc_expected))
kw_perc_exp_summary

>>>>

kids_kw_report_clean <- kids_kw_report %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  #filter(winter_id == 1) %>% 
  arrange(area, home_winter_id) %>% 
  mutate(filter_type = fct_collapse(filter_type,
                                    "Honeywell" = "Honeywell",
                                    "Large Filtrete" = "Large Filtrete",
                                    "Small Filtrete" = "Small Filtrete",
                                    "Winix" = c("Winix", "winix"))) %>% 
  mutate(kw_perc_expected = if_else(kw_hours == -999, 999999, kw_perc_expected),
         kw_perc_expected = if_else(kw_hours == 1000, 999999, kw_perc_expected),
         kw_perc_expected = abs(kw_perc_expected)) %>% 
  replace_with_na(replace = list(kw_perc_expected = 999999)) %>% 
  mutate(kw_perc_expected = as.numeric(kw_perc_expected)) %>% 
  filter(kw_perc_expected < 1000)

@@

kw_perc_exp_summary <- kids_kw_report_clean %>% 
  filter(!is.na(kw_perc_expected)) %>% 
  filter(winter_id == 1) %>% 
  #group_by(treatment_assigned) %>% 
  summarize("Mean KW % Exp" = mean(kw_perc_expected),
            "SD KW % Exp" = sd(kw_perc_expected),
            "N KW % Exp" = n(),
            "Min KW % Exp" = min(kw_perc_expected),
            "25Q KW % Exp" = quantile(kw_perc_expected, 0.25),
            "Med KW % Exp" = median(kw_perc_expected),
            "75Q KW % Exp" = quantile(kw_perc_expected, 0.75),
            "Max KW % Exp" = max(kw_perc_expected))
kw_perc_exp_summary
